\documentclass[10pt,a4paper]{article}
\usepackage[margin=1.45cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\setlist[itemize]{leftmargin=1.2em,itemsep=1pt,topsep=3pt,parsep=0pt}
\newcommand{\cvsection}[1]{\vspace{5pt}{\large\textbf{#1}}\par\vspace{2pt}\hrule\vspace{3pt}}

\begin{document}
\begin{center}
{\Large \textbf{Sofia Martin}}\\[2pt]
\textbf{Regulatory Affairs Specialist | Medical Devices | Lyon}\\[2pt]
sofia.martin@example.test | +33 4 00 00 00 00 | example.test/sofia
\end{center}

\cvsection{Profile}
Regulatory affairs specialist with three years of experience supporting medical-device compliance, technical documentation, notified-body submissions and post-market activities. Combines precise regulatory analysis with cross-functional coordination across quality, clinical and engineering teams.

\cvsection{Experience}
\textbf{MedNova Devices - Regulatory Affairs Associate} \hfill \textit{2023 - 2026}
\begin{itemize}
\item Prepared and maintained EU MDR technical documentation for Class II medical devices, including change-impact assessments and submission-readiness reviews.
\item Coordinated traceable evidence across quality, clinical and engineering teams and tracked notified-body questions through closure.
\item Supported post-market surveillance, vigilance reporting and updates to risk-management and clinical-evaluation documentation.
\end{itemize}
\textbf{BioCert Laboratories - Quality Assurance Intern} \hfill \textit{2022 - 2023}
\begin{itemize}
\item Reviewed controlled documents, training records and CAPA evidence against ISO 13485 procedures before internal audits.
\item Consolidated audit findings, owners and due dates into traceable follow-up packs for quality-management reviews.
\end{itemize}

\cvsection{Skills}
\textbf{Regulatory Affairs}: EU MDR, Class II medical devices, technical documentation, regulatory submissions, change control\\
\textbf{Quality Systems}: ISO 13485, CAPA, document control, internal audits\\
\textbf{Clinical \& Safety}: clinical evaluation, post-market surveillance, vigilance, risk management\\
\textbf{Professional Methods}: technical writing, gap analysis, traceability, stakeholder coordination

\cvsection{Education}
\textbf{University of Lyon - MSc Biomedical Engineering and Regulatory Affairs} \hfill \textit{2021 - 2023}\\
Medical-device regulation, quality systems, clinical evaluation and biostatistics.\\[2pt]
\textbf{University of Grenoble - BSc Life Sciences} \hfill \textit{2018 - 2021}\\
Cell biology, physiology, scientific writing and experimental design.

\cvsection{Certifications \& Training}
ISO 13485 Internal Auditor | EU MDR Technical Documentation | Good Clinical Practice

\cvsection{Professional Memberships}
Regulatory Affairs Professionals Society | French-speaking medical-device quality network

\cvsection{Languages}
French native | English C1 | German B1

\cvsection{Volunteering}
Volunteer science communicator for public workshops on medical-device safety and clinical research.
\end{document}
