\documentclass[10pt,a4paper]{article}
\usepackage[margin=1.45cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\setlist[itemize]{leftmargin=1.2em,itemsep=1pt,topsep=3pt,parsep=0pt}
\newcommand{\cvsection}[1]{\vspace{5pt}{\large\textbf{#1}}\par\vspace{2pt}\hrule\vspace{3pt}}

\begin{document}
\begin{center}
{\Large \textbf{Maya Laurent}}\\[2pt]
\textbf{Exhibition Producer | Cultural Programmes | Paris}\\[2pt]
maya.laurent@example.test | +33 1 00 00 00 02 | example.test/maya
\end{center}

\cvsection{Profile}
Exhibition producer with four years of experience coordinating cultural programmes, touring installations and public events. Combines production planning, budget control and partner management with a strong attention to visitor experience and accessible delivery.

\cvsection{Experience}
\textbf{Atelier Horizon - Exhibition Producer} \hfill \textit{2023 - 2026}
\begin{itemize}
\item Produced six temporary exhibitions from initial brief to opening, coordinating artists, curators, fabricators, venues and accessibility partners.
\item Managed production schedules, supplier consultations and budgets up to EUR 180,000, maintaining decision logs and weekly risk reviews.
\item Prepared installation plans, transport documentation, public-programme briefs and post-event reports for internal and external stakeholders.
\end{itemize}
\textbf{Maison des Cultures - Programme Coordinator} \hfill \textit{2021 - 2023}
\begin{itemize}
\item Coordinated a year-round programme of talks, workshops and performances across three venues, supporting more than 70 public events.
\item Built shared production calendars, artist welcome packs and audience feedback summaries, improving handovers between programming, technical and communications teams.
\end{itemize}

\cvsection{Selected Productions}
\textbf{City in Motion - Touring Installation} \hfill \textit{2025}\\
Coordinated three venue adaptations, lender agreements, transport, installation crews and opening-week public programming.\\[2pt]
\textbf{Night of Archives - Public Programme} \hfill \textit{2024}\\
Delivered a one-night programme for 1,200 visitors with 18 contributors, timed access, mediation teams and partner communications.

\cvsection{Professional Capabilities}
\textbf{Production}: schedules, budgets, procurement, logistics, installation planning, risk tracking\\
\textbf{Partnerships}: artists, curators, venues, suppliers, public institutions, community groups\\
\textbf{Programme Delivery}: event operations, visitor experience, accessibility, evaluation\\
\textbf{Communication}: briefs, contracts, reporting, facilitation, bilingual stakeholder coordination

\cvsection{Education}
\textbf{University of Paris - MA Cultural Project Management} \hfill \textit{2019 - 2021}\\
Cultural policy, production economics, audience development and project evaluation.\\[2pt]
\textbf{University of Lille - BA Art History} \hfill \textit{2016 - 2019}

\cvsection{Grants \& Awards}
Emerging Cultural Producer bursary | Sustainable Exhibition Design workshop

\cvsection{Professional Memberships}
French Association of Exhibition Professionals | ICOM emerging professionals network

\cvsection{Languages}
French native | English C1 | Spanish B2

\cvsection{Community Engagement}
Volunteer coordinator for monthly neighbourhood art workshops and open-studio events.
\end{document}
